Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays

### 2022-05-19 PrevAdjSurvey.tex
Updates from Overleaf
Overleaf bump

\abstract[Abstract]{To be written.}

\keywords{Class file; \LaTeXe; \emph{Wiley NJD}}

@@

Estimating and quantifying uncertainty for disease prevalence is a standard task in epidemiology.
For rare events, these estimates are highly sensitive to misclassification \cite{hemenwaySelfDefense}, making adjustments for sensitivity and specificity critically important.
While estimating prevalence (or any event proportion in a population) in complex surveys and adjusting estimates for misclassification have been well studied separately, performing both of these tasks simultaneously remains relatively unexplored.
A recent overview of methods for estimating prevalence in surveys without misclassification is provided by Dean and Pagano\cite{Dean:2015}.
For simple surveys with imperfect sensitivity and specificity, the method of Lang and Reiczigel\cite{Lang:2014} is the most recent advancement\cite{Flor2020}.
Fewer methods are available for for constructing frequentist confidence intervals for prevalence estimates from complex surveys while adjusting for sensitivity and specificity.
Kalish et al\cite{Kali:2021} developed one such method that is closely related to the method presented here, but their method's properties were not studied.
Another recent advancement is the method developed by Rosin et al \cite{rosin2021estimating} that 
 makes use of asymptotic normal approximations which reduce to the Wald interval when sensitivity and specificity are perfect.
This problem has also previously been addressed in Bayesian literature, recently by Gelman and Carpenter\cite{GelmanBayes}.

We work up to our ultimate goal in stages.
First, in Section~\ref{sec:srs-imperfect}, we propose confidence intervals for simple random samples where prevalence is assessed with an assay with imperfect sensitivity and/or specificity.
Next, in Section~\ref{sec:weight-perfect}, we present confidence intervals for weighted samples where prevalence is assessed with an assay without misclassification.
Finally, in Section~\ref{sec:weight-imperfect}, we combine these methods to create confidence intervals for weighted samples where prevalence is assessed with an assay with imperfect sensitivity and specificity.
Because the combined method reduces to one of the first two methods as a special case, we can think of the first two stages as testing the combined method in those cases. 
Our new method is designed to guarantee coverage in all situations, and we show through simulations that it beats the best competitors in each of the first two stages with respect to that property. For the last stage, the only competitor is 
very similar to our proposed method but had not previously been studied in detail, and both methods are nearly equivalent. Although the last stage presents some simulated scenarios where the coverage is anti-conservative, in most cases the new method does have proper coverage.

@@

\subsection{Notation and Problem Set-up}

To introduce notation, consider first the stratified simple random sample.
Suppose we have a survey with  \( k \) sampling units, with \( N_1, N_2, \ldots, N_k \) individuals in the population of unit \( i \).
We sample \( n_1, n_2, \ldots, n_k \) individuals via a simple random sample from each population to have an assay performed to determine who has a disease.
Let \( X_i \) be the number of positive results from an assay performed on the \( n_i \) individuals from sampling unit \( i \) and assume \( X_i \sim \operatorname{Binomial}(n_i, \theta_i) \), where \( \theta_i \) is the population frequency of positive results for assays performed on individuals from sampling unit \( i \).
Similarly, let \( X_i^* \) be the unobserved true number of people with the disease among the \( n_i \) individuals from sampling unit \( i \) and assume \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \), where \( \theta_i^* \) is the population frequency of cases in sampling unit \( i \).
In the case of a perfect assay, \( \theta_i = \theta_i^* \).

@@

\begin{equation}
    \beta^* = \frac{\sum_{i=1}^k N_i \theta_i^*}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \theta_i^*,
    \label{eq:pop-prev}
\end{equation}

@@

\begin{equation}
    \beta = \frac{\sum_{i=1}^k N_i \theta_i}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \theta_i,
    \label{eq:app-prev}
\end{equation}

where \( w_i = N_i / \sum_{j=1}^k N_j \) and, therefore, \( \sum_{i=1}^k w_i = 1 \).
This set-up will work for other complex survey samples, where we can treat the survey weights as known and each individual may be their own stratum.

We can relate $\theta_i$ and $\theta_i^*$ using the sensitivity ($\phi_p$)  and specificity (1-$\phi_n$) of the assay, 
where  $\phi_p$ and $\phi_n$  are the proportion of positive assays from a population of  positive controls (i.e., individuals known to have the disease) and 
negative controls (i.e., individuals known to be  without the disease), respectively. Then
$\theta_i = \phi_p \theta_i^* + \phi_n (1-\theta_i^*)$, or equivalently,  
\begin{eqnarray*}
\theta_i^* & = & \frac{ \theta_i - \phi_n }{\phi_p - \phi_n},
\end{eqnarray*}
and we have
\begin{align}
\begin{split}
  \beta^*   =&   \sum_{i=1}^k w_i \theta_i^* \\
            =&  \sum_{i=1}^k w_i \left( \frac{\theta_i - \phi_n}{\phi_p - \phi_n} \right) \\
            =&   \frac{\sum_{i=1}^k w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n \sum_{i=1}^k w_i}{\phi_p - \phi_n} \\
            =&   \frac{\sum_{i=1}^k w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n}{\phi_p - \phi_n}
            \label{eq:long-beta}
\end{split}
\end{align}

Suppose the assay is measured on \( m_n \) individuals known to not have the disease and on \( m_p \) individuals known to have the disease.
Let \( C_n \) and \( C_p \) be the number who test positive from the respective samples.
Assume that the negative and positive controls act like simple random samples from their respective populations.
Thus, \( C_n \sim \operatorname{Binomial}(m_n, \phi_n) \) where \( 1 - \phi_n \) is the specificity of the assay, and \( C_p \sim \operatorname{Binomial}(m_p, \phi_p) \), where  \( \phi_p \) is the sensitivity of the assay.
Let \( \hat{\theta}_i = \frac{X_i}{n_i} \), \( \hat{\phi}_n = \frac{C_n}{m_n} \), and \( \hat{\phi}_p = \frac{C_p}{m_p} \).
Then a plug-in estimator for \( \beta^* \) is 
\begin{equation}
    \hat{\beta}^* = \frac{\sum_{i=1}^k w_i \hat{\theta}_i}{\hat{\phi}_p - \hat{\phi}_n} - \frac{\hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n}. \label{eq:betastarhat}
\end{equation}

This estimator serves as an important basis for developing confidence intervals in this work.
Section~\ref{sec:srs-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( k = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e. estimating prevalence from a simple random sample with an imperfect assay.
Section~\ref{sec:weight-perfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e. estimating prevalence from a weighted sample with a perfect assay.
Section~\ref{sec:weight-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( k > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e. estimating prevalence from a weighted sample with an imperfect assay.

@@

First, we consider the scenario where \( k = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
We develop a confidence interval for the population prevalence, \( \beta^* \).
When \( k = 1 \), the estimand in Equation~\ref{eq:long-beta} becomes $\beta^* = (\theta_1 - \phi_n)/(\phi_p-\phi_n)$. We have $\phi_p > \phi_n$ for any useful assay, and when the sample is a mixture of individuals with and without the disease of interest, $\phi_p \geq \theta_1 \geq \phi_n$. The estimator of $\beta^*$ is 
%in Equation~\ref{eq:betastarhat} becomes

@@

Each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial probability parameter.
For each of these, we use distributions associated with  the exact binomial confidence interval.
For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution is \( \operatorname{Beta}(x, n - x + 1) \) with associated random variable \( B^L \), and the upper confidence distribution  is \( \operatorname{Beta}(x + 1, n - x)\) with random variable \( B^U \).
Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( 1 - \alpha \)\% central confidence interval of Clopper-Pearson\cite{10.1093/biomet/26.4.404} for the binomial parameter is 
\begin{equation}
\left\{ q \left( \frac{\alpha}{2}, B^L \right), q \left( 1 - \frac{\alpha}{2}, B^U, \right) \right\}.
\label{eq:C-P}
\end{equation}

@@

Next, we present a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
Our method is a straightforward adaptation of the gamma confidence interval presented in Fay and Feuer\cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to a weighted sum of Poisson rate parameters.
We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
Under this Poisson assumption, we suggest the \( 1 - \alpha \)\% gamma confidence interval for \( \beta^* \):

@@

\begin{equation*}
    y = \sum_{i=1}^k \frac{w_i}{n_i} x_i
\end{equation*}

\begin{equation*}
    v = \sum_{i=1}^k \left( \frac{w_i}{n_i}\right)^2 x_i
\end{equation*}

\begin{equation*}
    y^* = y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_k}{n_k} \right)
\end{equation*}

\begin{equation*}
    v^* = v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_k}{n_k} \right) \right\}^2
\end{equation*}

@@

with \( x_{\text{eff}} = n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i \), and \( n_{\text{eff}} \) defined in Equation~\ref{eq:neff}.
Although, Dean and Pagano \cite{Dean:2015} expressed this in terms of the F distributions, the beta distribution representation is equivalent.

@@

Lastly, we develop a confidence interval for the population prevalence, \( \beta^* \), in the case where \( k > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \).

@@

The alternative method is that used in Kalish, et al \cite{Kali:2021}.
We use the  modification of \cite{Korn:1998} presented in \cite{Dean:2015}, as in Section~\ref{sec:weight-perfect}, to derive the \( 1 - \alpha \)\% confidence interval for \( \beta^* \):

\begin{equation}
    \left\{ q \left( \frac{\alpha}{2}, \frac{B_{KG}^L - B_{\phi_n}^U }{B_{\phi_p}^U - B_{\phi_n}^U }  \right),  q \left( 1 - \frac{\alpha}{2}, \frac{B_{KG}^U - B_{\phi_n}^L}{B_{\phi_p}^L - B_{\phi_n}^L}  \right) \right\}.
\end{equation}

@@

@@

We assess and compare our new method (Melding) to that of Lang and Reiczigel (LR) in a variety of simulated settings.
In each simulation, 100 subjects are tested to estimate prevalence, 60 are tested to estimate sensitivity, and 300 are tested to estimate specificity.
Several combinations of prevalences (0.5\%--2\%), sensitivities (75\%--100\%) and specificities (75\%--100\%) are assessed.
Each simulated scenario is replicated 10,000 times.
Figure~\ref{fig:coverage_comparison_plot} compares the two methods based on coverage, while Figures~\ref{fig:lower_error_frequency_comparison_plot} and \ref{fig:upper_error_frequency_comparison_plot} present the lower and upper error frequencies for these scenarios, respectively.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/simple_coverage_comparison_plot.pdf}
    \caption{Coverage properties of 95\% confidence intervals for our new method (Melding) and the state of the art method (Lang-Reiczigel) in a variety of settings, each simulated 10,000 times.}
    \label{fig:coverage_comparison_plot}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/simple_lower_error_frequency_comparison_plot.pdf}
    \caption{Lower error properties of 95\% confidence intervals for our new method (Melding) and the state of the art method (Lang-Reiczigel) in a variety of settings, each simulated 10,000 times.}
    \label{fig:lower_error_frequency_comparison_plot}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/simple_upper_error_frequency_comparison_plot.pdf}
    \caption{Upper error properties of 95\% confidence intervals for our new method (Melding) and the state of the art method (Lang-Reiczigel) in a variety of settings, each simulated 10,000 times.}
    \label{fig:upper_error_frequency_comparison_plot}
\end{figure}

>>>>

\abstract[Abstract]{We present several related methods for creating confidence intervals to assess disease prevalence in variety of survey sampling settings. These include simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests, with the first two settings considered special cases of the third. Our methods use survey results and measurements of test sensitivity and specificity to construct melded confidence intervals. We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage. We apply our method to a seroprevalence survey of SARS-CoV-2 in undiagnosed adults in the United States between May and July 2020.}

\keywords{confidence distributions, seroprevalence, survey sampling, weighted sampling}

@@

Estimating and quantifying uncertainty for disease prevalence is a standard task in epidemiology.
For rare events, these estimates are highly sensitive to misclassification \cite{hemenwaySelfDefense}, making adjustments for sensitivity and specificity critically important.
While estimating prevalence (or any event proportion in a population) in complex surveys and adjusting estimates for misclassification have been well studied separately, performing both of these tasks simultaneously remains relatively unexplored.
Recent overviews of methods for estimating prevalence in surveys without misclassification are provided by Dean and Pagano\cite{Dean:2015} and Franco, et al\cite{franco2019}.
For  simple random sample surveys with imperfect sensitivity and specificity, Lang and Reiczigel\cite{Lang:2014} proposed an approximate method that performed well in simulations. Recent work by DiCiccio, et al \cite{DiCi:2021} and Cai et al \cite{Cai:2020} study both valid (i.e., exact) and approximate methods. Their valid methods use test inversion and the adjustment of Berger and Boos \cite{Berg:1994}, while their approximation methods use the bootstrap with the test inversion approach. 
Fewer methods are available for for constructing frequentist confidence intervals for prevalence estimates from complex surveys while adjusting for sensitivity and specificity.
Kalish et al\cite{Kali:2021} developed one such method that is closely related to one of the methods presented here, but that method's properties were not studied.
Cai et al \cite{Cai:2020} (see also discussion in DiCiccio et al \cite{DiCi:2021}) modify their approximation approach to allow sample weights, but it assumes that the number of counts of events within the strata are large (see their Remark 4).  Thus, it would not apply to a weighted survey method where each individual their own weight. 
Another recent advancement is the method developed by Rosin et al \cite{rosin2021estimating} that 
 makes use of asymptotic normal approximations which reduce to the Wald interval when sensitivity and specificity are perfect.
This problem has also previously been addressed in Bayesian literature, recently by Gelman and Carpenter\cite{GelmanBayes}.

We work up to our ultimate goal in stages.
First, in Section~\ref{sec:srs-imperfect}, we propose confidence intervals for simple random samples where prevalence is assessed with an assay with imperfect sensitivity and/or specificity.
Next, in Section~\ref{sec:weight-perfect}, we present confidence intervals for weighted samples where prevalence is assessed with an assay without misclassification.
In Section~\ref{sec:weight-imperfect}, we combine these methods to create confidence intervals for weighted samples where prevalence is assessed with an assay with imperfect sensitivity and specificity.
Because the combined method reduces to one of the first two methods as a special case, we can think of the first two stages as testing the combined method in those cases.  Finally, in Section~\ref{sec:complex-surveys} we show how certain complex surveys may fit into the format for our new method.
Our new method is designed to guarantee coverage in all situations.

In simulations we compare our method to established frequentist competitors.
and  show through simulations that it beats the best of those in each of the three stages with respect to guaranteeing coverage. 
We did not include in our simulations the new methods that have been developed in response to the COVID-19 pandemic and are not yet in print in peer reviewed journals \cite{Cai:2020,DiCi:2021,rosin2021estimating}.
The exact method of DiCiccio, et al \cite{DiCi:2021} would guarantee coverage, although applying it to a survey with a large number of strata would be ``computationally expensive'', and it has not been applied to surveys using post-stratification weighting. In contrast, our new method can very tractable in those situations.

@@

\subsection{Notation and Problem Set-up}
\label{sec-notation}

To introduce notation, consider first the stratified simple random sample.
Suppose we have a population partitioned into   \( K \) strata, with \( N_1, N_2, \ldots, N_K \) individuals in the  K strata of the population.
We sample \( n_1, n_2, \ldots, n_K \) individuals via a simple random sample from each of the \( K \)  strata to have an assay performed to determine who has a disease.
Let \( X_i \) be the number of positive results from an assay performed on the \( n_i \) individuals from stratum \( i \) and assume \( X_i \sim \operatorname{Binomial}(n_i, \theta_i) \), where \( \theta_i \) is the population frequency of positive results for assays performed on individuals from stratum \( i \).
Similarly, let \( X_i^* \) be the unobserved true number of people with the disease among the \( n_i \) individuals from stratum  \( i \) and assume \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \), where \( \theta_i^* \) is the population frequency of cases in stratum \( i \).
In the case of a perfect assay, \( \theta_i = \theta_i^* \).

@@

\begin{equation}
    \beta^* = \frac{\sum_{i=1}^K N_i \theta_i^*}{\sum_{j=1}^K N_j} = \sum_{i=1}^K w_i \theta_i^*,
    \label{eq:pop-prev}
\end{equation}

@@

\begin{equation}
    \beta = \frac{\sum_{i=1}^K N_i \theta_i}{\sum_{j=1}^K N_j} = \sum_{i=1}^K w_i \theta_i,
    \label{eq:app-prev}
\end{equation}

where \( w_i = N_i / \sum_{j=1}^K N_j \) and, therefore, \( \sum_{i=1}^K w_i = 1 \).
This set-up will approximately work for other complex survey samples, where we can estimate survey weights such that the complex survey sample may be treated as a multinomial sample with probabilities proportional to those weights  (see Section~\ref{sec:complex-surveys}).

We can relate $\theta_i$ and $\theta_i^*$ using the sensitivity ($\phi_p$)  and specificity (1-$\phi_n$) of the assay, 
where  $\phi_p$ and $\phi_n$  are the proportion of positive assays from a population of  positive controls (i.e., individuals known to have the disease) and 
negative controls (i.e., individuals known to be  without the disease), respectively. Then
$\theta_i = \phi_p \theta_i^* + \phi_n (1-\theta_i^*)$, or equivalently,  
\begin{eqnarray*}
\theta_i^* & = & \frac{ \theta_i - \phi_n }{\phi_p - \phi_n},
\end{eqnarray*}
and we have
\begin{align}
\begin{split}
  \beta^*   =&   \sum_{i=1}^K w_i \theta_i^* 
            =  \sum_{i=1}^K w_i \left( \frac{\theta_i - \phi_n}{\phi_p - \phi_n} \right) \\
            =&   \frac{\sum_{i=1}^K w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n \sum_{i=1}^K w_i}{\phi_p - \phi_n} 
            =   \frac{\sum_{i=1}^K w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n}{\phi_p - \phi_n}
            \label{eq:long-beta}
\end{split}
\end{align}

Suppose the assay is measured on \( m_n \) individuals known to not have the disease and on \( m_p \) individuals known to have the disease.
Let \( C_n \) and \( C_p \) be the number who test positive from the respective samples.
Assume that the negative and positive controls act like simple random samples from their respective populations.
Thus, \( C_n \sim \operatorname{Binomial}(m_n, \phi_n) \) where \( 1 - \phi_n \) is the specificity of the assay, and \( C_p \sim \operatorname{Binomial}(m_p, \phi_p) \), where  \( \phi_p \) is the sensitivity of the assay.
Let \( \hat{\theta}_i = \frac{X_i}{n_i} \), \( \hat{\phi}_n = \frac{C_n}{m_n} \), and \( \hat{\phi}_p = \frac{C_p}{m_p} \).
Then a plug-in estimator for \( \beta^* \) is 
\begin{equation}
    \hat{\beta}^* = \frac{\sum_{i=1}^K w_i \hat{\theta}_i}{\hat{\phi}_p - \hat{\phi}_n} - \frac{\hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n}. \label{eq:betastarhat}
\end{equation}

This estimator serves as an important basis for developing confidence intervals in this work.
Section~\ref{sec:srs-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e. estimating prevalence from a simple random sample with an imperfect assay.
Section~\ref{sec:weight-perfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e. estimating prevalence from a weighted sample with a perfect assay.
Section~\ref{sec:weight-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e. estimating prevalence from a weighted sample with an imperfect assay.

@@

First, we consider the scenario where \( K = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
We develop a confidence interval for the population prevalence, \( \beta^* \).
When \( K = 1 \), the estimand in Equation~\ref{eq:long-beta} becomes $\beta^* = (\theta_1 - \phi_n)/(\phi_p-\phi_n)$. We have $\phi_p > \phi_n$ for any useful assay, and since the sample is a mixture of individuals with and without the disease of interest, $\phi_p \geq \theta_1 \geq \phi_n$. The estimator of $\beta^*$ is 
%in Equation~\ref{eq:betastarhat} becomes

@@

Each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial probability parameter.
For each of these, we use distributions associated with  the exact binomial confidence interval.
For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution is \( \operatorname{Beta}(x, n - x + 1) \) with associated random variable \( B^L \), and the upper confidence distribution  is \( \operatorname{Beta}(x + 1, n - x)\) with random variable \( B^U \), where for $a>0$ we let \( \operatorname{Beta}(0,a) \) and \( \operatorname{Beta}(a,0) \) be point masses at 0 and 1, respectively.
Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( 1 - \alpha \)\% central confidence interval of Clopper-Pearson\cite{10.1093/biomet/26.4.404} for the binomial parameter is 
\begin{equation}
\left\{ q \left( \frac{\alpha}{2}, B^L \right), q \left( 1 - \frac{\alpha}{2}, B^U, \right) \right\}.
\label{eq:C-P}
\end{equation}

@@

Next, we present a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( K > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
Our method is a straightforward adaptation of the gamma confidence interval presented in Fay and Feuer\cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to be a weighted sum of Poisson rate parameters.
We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
Under this Poisson assumption, we suggest the \( 100(1 - \alpha) \)\% gamma confidence interval for \( \beta^* \):

@@

\begin{equation*}
    y = \sum_{i=1}^K \frac{w_i}{n_i} x_i
\end{equation*}

\begin{equation*}
    v = \sum_{i=1}^K \left( \frac{w_i}{n_i}\right)^2 x_i
\end{equation*}

\begin{equation*}
    y^* = y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right)
\end{equation*}

\begin{equation*}
    v^* = v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right) \right\}^2.
\end{equation*}

@@

with \( x_{\text{eff}} = n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i \), and \( n_{\text{eff}} \) defined in Equation~\ref{eq:neff}.
Although Dean and Pagano \cite{Dean:2015} expressed this in terms of the F distributions, the beta distribution representation is equivalent.

@@

Lastly, we develop a confidence interval for the population prevalence, \( \beta^* \), in the case where \( K > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \).

@@

The alternative method is very similar to that used in Kalish, et al \cite{Kali:2021}.
We use the  modification of \cite{Korn:1998} presented in \cite{Dean:2015}, as in Section~\ref{sec:weight-perfect}, to derive the \( 100(1 - \alpha) \)\% confidence interval for \( \beta^* \):

\begin{equation}
    \left\{ q \left( \frac{\alpha}{2}, g\left[B_{KG}^L, B_{\phi_n}^U, B_{\phi_p}^U\right]  \right),  q \left( 1 - \frac{\alpha}{2}, g\left[B_{KG}^U, B_{\phi_n}^L, B_{\phi_p}^L\right]  \right) \right\}.
\end{equation}

@@

\subsection{Applications to More Complex Surveys}
\label{sec:complex-surveys}

\subsubsection{When Can We Use These Methods}

In Section~\ref{sec-notation}, we derived methods assuming that the apparent prevalence was a weighted sum of binomial random variables,
$\beta = \sum_{i=1}^{K} w_i \frac{X_i}{n_i}$, where $X_i \sim \textrm{Binomial}(n_i,\theta_i)$. We used the fact that for small $\theta_i$ and large $n_i$
the binomial can be approximated by the Poisson, giving $X_i \stackrel{\cdot}{\sim} \textrm{Poisson}( n_i \theta_i)$.
Thus, whenever we can model a complex survey estimator of apparent prevalence as a weighted sum of Poisson variates, then we can apply the methods of this paper.

In the upcoming Section~\ref{sec-MultPoisson}, we give a detailed review relating the multinomial sampling model  to a weighted sum of Poisson variates model.
The multinomial sampling model treats the survey sample as if it is a sampling with replacement from the entire population of $N$ individuals, where each of the $N$
individuals has a probability of $P_j$ of being sampled for each of the $n$ samples from the survey, with $\sum_{j=1}^{N} P_j = 1$. Under this model the number of times each of the $N$ individuals
is included in the sample is a multinomial with parameters $n$ and $[P_1,\ldots, P_N]$.
The multinomial model describes sampling with replacement, but it is nevertheless used to approximate a sampling design where the $j$th  individual is sampled {\it without} replacement with probability $P_j$, even though under that design (unlike the multinomial model) no individual is included in the sample more than once. The multinomial model is a common approximation for other complex survey designs; \citep[see e.g., ][p. 14]{Korn:1999}.
For example, in the  Kalish, et al\cite{Kali:2021} analysis of Section~\ref{sec-Application} each individual in the sample is assigned a pseudo-weight approximating one over their sampling probability from
a multinomial model. The actual sample was not a probability sample. In fact, it was a quota sample from a very large pool of self-selected volunteers, and the pseudo-weights were calculated using a different large survey that was a probability weighted survey. The pseudo-weights were calculated such that if they were analyzed under the multinomial model, they would adjust for selection bias due to self-selection of the volunteers and the imperfection of the quota sampling.

\subsubsection{Multinomial Sampling Model}
\label{sec-MultPoisson}

Let $Y_1,\ldots, Y_N$ be the binary indicators of event in the $N$ individuals  in the population of interest,
so the prevalence is $\beta = N^{-1} \sum_{j=1}^{N} Y_j$. There are many ways to design a complex survey sample, and it is often useful to analyze them as if
individuals were sampled with replacement with the sampling probability of the $j$th  individual equal to $P_j$, with $\sum_{j=1}^{N} P_j = 1$
In other words, we treat the sample as if it was $n$ independent multinomial samples each with one trial and selection probability vector  $[P_1,\ldots, P_N]$.
Let $I_{ij}=1$ if the $i$th draw for the sample is individual $j$ in the population, and $0$ otherwise. Then let $y_i = Y_j$ and $p_i=P_j$ when $I_{ij}=1$.
Here, following the tradition in the survey literature, we use capital letters for the population of interest (e.g., N,Y,P), and lower case letters for the sample (e.g., n,y,p).
In this notation, both $y_i$ and $Y_j$ are fixed, and only the variables representing the sampling (i.e., the $I_{ij}$ variables) are random.
Under this independent multinomial model, since $E(I_{ij})=P_j$, an unbiased estimator of $\beta$ is
\begin{eqnarray}
\hat{\beta} & = & \frac{1}{n} \sum_{i=1}^{n} \frac{ y_i}{N p_i} = \frac{1}{n} \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j}
\label{eq:betahatMultinomial}
\end{eqnarray}
and an unbiased estimator of $\textrm{var}(\hat{\beta})$ under the multinomial model is
\begin{eqnarray}
\widehat{\textrm{var}}_{M}(\hat{\beta}) & = & \frac{1}{n (n-1)} \sum_{i=1}^{n} \left( \frac{y_i}{Np_i} - \hat{\beta}  \right)^2
\label{eq:varMbetahat}
\end{eqnarray}
(see Korn and Graubard \cite{Korn:1999} Problem 2.2-10). We can write $\hat{\beta}$ as a weighted sum. Traditional survey weighting defines the weights so that
the weight for the $i$th sampled individual can be interpreted as the number of individuals in the population that the $i$th sampled individual represents.
Following that tradition, let   $w_i^{(trad)}= 1/(np_i)$ and $W_j^{trad)}=1/(nP_j)$, then the expected sum of the sampled weights is $N$,
\begin{eqnarray*}
E \left( \sum_{i=1}^{n} w_i^{(trad)} \right)  & = & E \left(  \sum_{i=1}^{n} \sum_{j=1}^{N} I_{ij} W_j^{(trad)} \right) =    \sum_{i=1}^{n} \sum_{j=1}^{N} \frac{ E(I_{ij})}{ n P_j} =   \sum_{i=1}^{n} \sum_{j=1}^{N} \frac{1}{n} = N.
\end{eqnarray*}
Sometimes the weights are scaled after selection so that the scaled weights are $w_i^{(strad)} = \frac{ N w_i^{(trad)} }{\sum_{i=1}^{n} w_i^{(trad)}}$ and are forced to sum to $N$.
For example, in Kalish et al \cite{Kali:2021} rescaling (sometimes called post-stratification) was done in a more complicated manner to ensure that the weights summed to the US census population within age group, sex, race, ethnicity and region.

For this paper we define the weights differently, because we want to model our estimator as a weighted sum of Poisson random variables.
Thus, we use $w_i = 1/(nNp_i)$ and $W_j= 1/(nNP_j)$ so that the sums have expectation $1$.
In the complex survey case,
we start with the independent multinomial model as in equation~\ref{eq:betahatMultinomial}, then we use the relationship between the multinomial and Poisson distributions.
Using the ``multinomial-Poisson transformation'', the maximum
likelihood estimates (MLE) for a multinomial random variable are equivalent to the MLEs for independent Poisson random variables, and
the variances are asymptotically equivalent (see Baker\cite{Baker:1994}).
Even though we model $\hat{\beta}$ using multinomial random variables where there are many missing values (which occurs in our situation whenever $I_{ij}=0$),
that multinomial-Poisson relationship holds even when there are missing variables (see Baker\cite{Baker:1994}, Section 3).
For both the Poisson and multinomial models, $E(I_{ij}) = P_j$, and $\hat{\beta}$ is unbiased under either model.
For the Poisson model, all the $I_{ij}$ are independent and each mean equals its variance, so that the variance of $\hat{\beta}$ under this model is
\begin{eqnarray*}
\textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left(  \frac{1}{n}  \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j} \right)  \\
& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
\end{eqnarray*}
We estimate $\textrm{var}_P \left(\hat{\beta} \right)$ by multiplying each term in the sum by $I_{ij}/P_j$, which has an expectation of $1$ and eliminates terms of non-selected individuals, giving
\begin{eqnarray}
\widehat{\textrm{var}}_P \left(\hat{\beta} \right)
& = &   \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{n^2 N^2 P_j^2}  =  \sum_{i=1}^{n}  \frac{  y_i}{n^2 N^2 p_i^2} \label{eq:hatvarbetahat1}
\end{eqnarray}
Under the Poisson model $\widehat{\textrm{var}}_P \left(\hat{\beta} \right)$ is an unbiased estimator of $\textrm{var}_P \left(\hat{\beta} \right)$.

@@

We assess and compare our new method (Melding, i.e., equation~\ref{eq:srs-conf-int}) to that of Lang and Reiczigel (LR) in a variety of simulated settings.
In each simulation, 100 subjects are tested to estimate prevalence, 60 are tested to estimate sensitivity, and 300 are tested to estimate specificity.
Several combinations of prevalences (0.5\%--2\%), sensitivities (75\%--100\%) and specificities (75\%--100\%) are assessed.
Each simulated scenario is replicated 10,000 times.
Figure~\ref{fig:coverage_comparison_plot} compares the two methods based on coverage, while Figures~\ref{fig:lower_error_frequency_comparison_plot} and \ref{fig:upper_error_frequency_comparison_plot} present the lower and upper error frequencies for these scenarios, respectively.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/simple_coverage_comparison_plot.pdf}
    \caption{Coverage properties of 95\% confidence intervals for our new method (Melding) and the Lang-Reiczigel method in a variety of settings, each simulated 10,000 times.}
    \label{fig:coverage_comparison_plot}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/simple_lower_error_frequency_comparison_plot.pdf}
    \caption{Lower error properties of 95\% confidence intervals for our new method (Melding) and the Lang-Reiczigel method in a variety of settings, each simulated 10,000 times.}
    \label{fig:lower_error_frequency_comparison_plot}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/simple_upper_error_frequency_comparison_plot.pdf}
    \caption{Upper error properties of 95\% confidence intervals for our new method (Melding) and the Lang-Reiczigel method in a variety of settings, each simulated 10,000 times.}
    \label{fig:upper_error_frequency_comparison_plot}
\end{figure}
